Geometry of Ranked Nearest Neighbour Interchange Space of Phylogenetic Trees

### 2019-12-30 rnni_convexity.tex
Mareike came to Max Plank too!
add ranks fig 1
caption fig2: blue->dashed

\begin{figure}[H]
\centering
\includegraphics[width=0.25\textwidth]{ranked_tree}
\vspace{12pt}
\caption{A ranked tree with $6$ taxa.}
\label{fig:ranked_tree}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{RNNI}
\vspace{12pt}
\caption{Two types of operation that define edges of the $\rnni$ graph.
The rank move swaps the rank of the two highlighted nodes and the $\nni$ moves are performed on the blue edges.}
\label{fig:RNNI}
\end{figure}

@@

Part of this work was done while LC and AG were visiting Max Plank Institute for Evolutionary Biology, we appreciate their support.

>>>>

\begin{figure}[H]
\centering
\includegraphics[width=0.4\textwidth]{ranked_tree}
\vspace{12pt}
\caption{A ranked tree with $6$ taxa.}
\label{fig:ranked_tree}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{RNNI}
\vspace{12pt}
\caption{Two types of operation that define edges of the $\rnni$ graph.
The rank move swaps the rank of the two highlighted nodes and the $\nni$ moves are performed on the dashed edges.}
\label{fig:RNNI}
\end{figure}

@@

Part of this work was done while AG, LC, and MF were visiting Max Plank Institute for Evolutionary Biology, we appreciate their support.
